\documentclass[11pt,draftnofoot,onecolumn]{IEEEtran}

\def\spacingset#1{\def\baselinestretch{#1}\small\normalsize}

%\def\ninept{\def\baselinestretch{.95}\let\normalsize\small\normalsize}

\setlength{\topmargin}{-0.4in}             % Move the top margin up with the negative value.
\setlength{\textheight}{9.0in}                % Set the hight of the text.
\setlength{\textwidth}{6.9in}               % Set the width of the text.
\setlength{\oddsidemargin}{-0.2in}           % Set the odd side left margin; useful for the double-sided case.
\setlength{\evensidemargin}{-0.2in}

%\parskip=1pt
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{epsf}
%\usepackage{psfig}
\usepackage{graphicx}
%\usepackage{showkeys}
\input{../commonFiles/comdefs}


\begin{document}

\spacingset{1.5}


\title{Be Cautious when Using the FIR Channel Model\\
with the OFDM-Based Communication Systems}

%\ninept%
%
\author{\IEEEauthorblockN{Jianhua Liu}
\IEEEauthorblockA{Department of Electrical and Systems Engineering\\
Embry-Riddle Aeronautical University\\
Daytona Beach, FL 32114\\
Email: Jianhua.Liu@erau.edu}
%
}
%
%
\maketitle%
%


\section*{Abstract}

Orthogonal frequency-division multiplexing (OFDM) 
can be used
to support high data rate transmissions over time-dispersive fading
channels. Many OFDM-based communication systems use packet-based
transmission, where channel estimation is needed for the detection
of the information-carrying symbols. The finite impulse response
(FIR) channel model is simple and effective for some simulations of
the OFDM-based communication systems over the time-dispersive
channels; yet, it is only an approximate channel model which cannot
be used in the case of accurate channel estimation. Unfortunately,
many researchers have overlooked this issue and have been devising
channel estimation algorithms squarely based on the FIR channel
model. While the channel estimation results from these algorithms
can be impressive for the FIR channels, the algorithms can hardly be
applied in real-world applications. This paper explains in detail
the reason why the FIR channel model is only an approximate one for
the OFDM-based communication systems, 
trying to discourage the inappropriate usage
of this model, which can lead to fruitless efforts. This paper also
presents a realistic channel model for the OFDM-based communication
systems, which can be used to access the channel parameter
estimation algorithms
realistically.%


\section*{ Index Terms}

OFDM, channel model, channel estimation


\section*{Important Contributions}

This paper explicitly indecates that the FIR channel model cannot accurately
characterize the channels for the OFDM-based systems. Therefore
caution is needed when using this model for the OFDM-based systems.
It is especially not appropriate to design channel estimation
algorithms for the OFDM-based system squarely based on this model;
when this model is not appropriate, the modified exponential channel
model can be used.


\section*{Impotant Citations}

\begin{itemize}

\item \cite{Chayat1997} proposed an FIR (finite impulse response)
filter channel model for the simulation of the time-dispersive fading channels for the
OFDM-based communication systems.

\item \cite{LiuLi2004} used a non-FIR channel for channel estimation as the FIR channel model is not appropriate for channel estimation. 

\end{itemize}


\bibliographystyle{ieeetr}
\bibliography{../commonFiles/all}


\end{document}
