\documentclass[11pt,draftnofoot,onecolumn]{IEEEtran}

\def\spacingset#1{\def\baselinestretch{#1}\small\normalsize}

%\def\ninept{\def\baselinestretch{.95}\let\normalsize\small\normalsize}

\setlength{\topmargin}{-0.4in}             % Move the top margin up with the negative value.
\setlength{\textheight}{9.0in}                % Set the hight of the text.
\setlength{\textwidth}{6.9in}               % Set the width of the text.
\setlength{\oddsidemargin}{-0.2in}           % Set the odd side left margin; useful for the double-sided case.
\setlength{\evensidemargin}{-0.2in}

%\parskip=1pt
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{epsf}
%\usepackage{psfig}
\usepackage{graphicx}
%\usepackage{showkeys}
\input{../commonFiles/comdefs}


\begin{document}

\spacingset{1.5}


\title{Parameter Estimation and Error Reduction for OFDM Based WLANs}
%\ninept%
%
%\spacingset{1.127}
\author{\IEEEauthorblockN{Jianhua Liu}
\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
P.O. Box 116130\\
University of Florida\\
Gainesville, FL 32611-6130} %
\and \IEEEauthorblockN{Jian Li}
\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
P.O. Box 116130\\
University of Florida\\
Gainesville, FL 32611-6130}%
}
%
%
\maketitle%
%


\section*{Abstract}

We consider parameter estimation and error reduction for
orthogonal frequency-division multiplexing 
(OFDM) based high-speed
wireless local area networks (WLANs).
We devise or select algorithms that can provide benefit to the 
{\em overall} system performance and can be efficiently
implemented in real-time. In particular,
first, we give a channel model which 
is especially useful for assessing
the channel parameter estimation methods devised for OFDM based WLANs. 
Second, we provide  
a sequential method for the estimation 
of carrier frequency offset (CFO), symbol timing, and channel response, 
by exploiting the structure of the packet
preamble specified by the IEEE 802.11a standard.
Finally, %we account for the aforementioned various errors: 
to correct the residue CFO induced phase error using the pilot tones, 
we consider maximum-likelihood phase tracking and 
least-squares phase fitting approaches;
to improve the channel estimation accuracy using
the decoded data, we present a semi-blind
channel estimation method; 
to mitigate the sampling clock induced 
time delay error, we provide a 
sampling clock synchronization approach 
that obviates the need of an automatic frequency control
clock recovery circuit.
The overall system performance of using our algorithms is demonstrated 
via several numerical examples.


\section*{ Index Terms}

OFDM, WLAN, channel model, 
symbol timing, carrier synchronization,
channel estimation, pilot tones, 
sampling clock synchronization, WLAN standards.


\section*{Important Contributions}

We have devised or selected channel parameter estimation and error 
reduction algorithms to improve the overall system performance
for the OFDM based WLANs and to be readily implemented in real-time. 
In particular, first, we have given a channel model which can be used to
characterize the true channels for the OFDM signaling.
Second, by exploiting the structure of the packet
preamble specified by the IEEE 802.11a standard, 
we have provided a sequential method for the estimation 
of CFO, symbol timing, and channel response.
Unlike some of the existing channel parameter estimation methods, 
our method works well for the true channels and is 70 times more 
efficient than an existing method.
Finally, to correct the CPE
using the pilot tones, we have considered ML phase tracking and 
LS phase fitting approaches. The proper phase fitting
can yield a gain of up to 1.2 dB. 
Moreover, a semi-blind
channel estimation method has been presented to improve
the channel estimation accuracy, which results in an additional
gain of up to 1.5 dB. 
Furthermore, to correct the sampling clock error, we have provided a 
sampling clock synchronization approach that avoids the use
of an AFC circuit. The algorithms given herein
can be readily extended to the case of multiple receive antennas.
We are currently implementing our algorithms
on the DSP hardware.


\section*{Impotant Citations}

\begin{itemize}

\item \cite{Chayat1997} proposed an FIR (finite impulse response)
filter channel model for the simulation of the time-dispersive fading channels for the
OFDM-based communication systems.


\end{itemize}


\bibliographystyle{ieeetr}
\bibliography{../commonFiles/all}


\end{document}
