\documentclass[11pt,draftnofoot,onecolumn]{IEEEtran}

\def\spacingset#1{\def\baselinestretch{#1}\small\normalsize}

%\def\ninept{\def\baselinestretch{.95}\let\normalsize\small\normalsize}

\setlength{\topmargin}{-0.4in}             % Move the top margin up with the negative value.
\setlength{\textheight}{9.0in}                % Set the hight of the text.
\setlength{\textwidth}{6.9in}               % Set the width of the text.
\setlength{\oddsidemargin}{-0.2in}           % Set the odd side left margin; useful for the double-sided case.
\setlength{\evensidemargin}{-0.2in}

%\parskip=1pt
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{epsf}
%\usepackage{psfig}
\usepackage{graphicx}
%\usepackage{showkeys}
\input{../commonFiles/comdefs}


\begin{document}

\spacingset{1.5}


\title{Channel Estimation for an OFDM-Based MIMO System}
%\ninept%
%
%\spacingset{1.127}
\author{\IEEEauthorblockN{Jianhua Liu}
\IEEEauthorblockA{Department of Electrical and Systems Engineering\\
Embry-Riddle Aeronautical University\\
Daytona Beach, FL 32114\\
Email: Jianhua.Liu@erau.edu} %
\and \IEEEauthorblockN{Jian Li}
\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
P.O. Box 116130\\
University of Florida\\
Gainesville, FL 32611-6130}%
}
%
%
\maketitle%
%


\section*{Abstract}

We consider the problem of channel estimation for an orthogonal
frequency-division multiplexing (OFDM)-based multiple-input
multiple-output (MIMO) wireless local area network system. We show
that an existing channel estimation approach, which is based on a
sub-carrier level orthogonal training symbol design and the finite
impulse response channel model, can suffer from severe performance
degradations for realistic OFDM channels. As such, we propose a new
channel estimation approach, which employs a modified version of
this training symbol design and a polynomial fitting/interpolation
method. Our simulation results show that our new channel estimation
approach significantly outperforms the existing one for the
realistic OFDM channels.


\section*{ Index Terms}

Channel estimation, OFDM, MIMO system, Wireless LAN standards.


\section*{Important Contributions}

This paper argues that the FIR channel model cannot accurately
characterize the channels for the OFDM-based systems but is a good choice for simple system performance simulations.

Based on this augument, this paper proposes a new channel estimation approach,
a polynomial fitting/interpolation
method based on a modified training symbol design,
for an OFDM-based MIMO WLAN system.
Simulation results have
shown that the new channel estimation approach can significantly
outperform existing ones.


\section*{Impotant Citations}

\begin{itemize}

\item \cite{Chayat1997} proposed an FIR (finite impulse response)
filter channel model for the simulation of the time-dispersive fading channels for the
OFDM-based communication systems.

\item \cite{LiuLi2004} used a non-FIR channel for channel estimation as the FIR channel model is not appropriate for channel estimation. 

\item \cite{WangLiu2002} uses polynomial approximation of the channel.


\end{itemize}


\bibliographystyle{ieeetr}
\bibliography{../commonFiles/all}


\end{document}
